\documentclass[10pt,a4paper,ragged2e]{altacv}

% Change the page layout
\geometry{left=2cm,right=10cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}

% Change the font
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Carlito}
\else
  % If using pdflatex:
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

% Change the colours
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\addbibresource{sample.bib}

\begin{document}
\name{Carter Nesbitt}
\tagline{Computer Engineering}
\personalinfo{
   \email{ccnesbitt@gmail.com}
   \phone{518-307-4096}
%  \mailaddress{Address, Street, 00000 County}
   \location{Rochester Institute of Technology}
%  \homepage{}
%  \twitter{}
%  \linkedin{linkedin.com/in/carter-nesbitt-343541165}
   \github{github.com/cjn9414}
}

\begin{fullwidth}
\makecvheader
\end{fullwidth}

\AtBeginEnvironment{itemize}{\small}

\cvsection[resume-sidebar]{Education}
\cvevent{Bachelor's of Science - GPA: 3.99}{Rochester Institute of Technology}{Graduating June 2022}{}

\cvsection{Experience}

\cvevent{Firmware Engineering Intern}{Positive Science}{Feb 2019 -- Aug 2019}{Rochester, NY}
\begin{itemize}
\item Research, development and integration of various sensors and components onto an embedded system.
\smallskip
\item Worked on a small team to diagnose and resolve issues in both software and hardware that cause device failures.
\smallskip
\item Leading firmware development, device diagnostics and research of system during internship.
\smallskip
\item Experience with internal and wireless communications, operating systems, and constraints associated with embedded systems.
\end{itemize}

\divider

\cvevent{Orientation Programming Assistant}{Rochester Institute of Technology}{Mar 2019 -- Aug 2019}{Rochester, NY}
\begin{itemize}
\item Organized and maintained a welcoming campus for new students arriving at RIT.
\smallskip
\item Setup and supervised many events that took place during RIT's orientation week.
\item Collaborated with a close team to maintain a reputable New Student Orientation program at RIT.
\end{itemize}

\divider

\cvevent{Orientation Leader}{Rochester Institute of Technology}{August 2018}{Rochester, NY}
\begin{itemize}
\item Provided guidance to a group of new students during their first weeks at university.
\smallskip
\item Gave advice with respect to college life and critical habits to new students to aid in their personal development at RIT.
\item Functioned as part of the public view of RIT under the New Student Orientation program.
\end{itemize}

\cvsection{Achievements}
\smallskip
\begin{itemize}
\item Maintained Dean's List at RIT every semester, beginning Fall 2017.
\item Computer Engineering Department GPA of 4.0
\end{itemize}

\clearpage

\nocite{*}

\end{document}
